Towards Compiler-Agnostic Performance in Finite-Difference Codes

### 2015-09-14 docs/papers/shallow_performance/shallow_perf.tex
parco paper: re-worded paragraph describing transormations required by Gnu compiler

With the Gnu compiler (first and third clusters in
Figure~\ref{FIG_opt_stages_256}), the vanilla \psykal\ version of
Shallow only achieves ~5-6\% of the performance of the
original. Simply copying the code for each of the kernel subroutines
into the module from which they are called (module in-lining) has the
most dramatic effect on the performance of the compiled code; it now
achieves more than 80\% of the performance of the original. The
transformations required to get beyond this level then become
architecture dependent: on Haswell loop fusion achieves more than 90\%
while on Ivy Bridge it is fully-fusing the first loop nest. The
dramatic performance improvement obtained from the module-inlining
transformation demonstrates that the Gnu compiler is unable to
optimise over separate files.

>>>>

With the Gnu compiler (first and third clusters in
Figure~\ref{FIG_opt_stages_256}), the vanilla \psykal\ version of
Shallow only achieves ~5-6\% of the performance of the
original. Simply copying the code for each of the kernel subroutines
into the module from which they are called (module in-lining) has the
most dramatic effect on the performance of the compiled code; it now
achieves more than 80\% of the performance of the original. The
transformation(s) required to get more than 90\% then become
architecture dependent: on Haswell it is just loop fusion while on Ivy
Bridge we do not exceed 90\% until we have done all of the steps up to
and including fully-fusing (fusing the inner loops of) the first loop
nest. The dramatic performance improvement obtained from the
module-inlining transformation demonstrates that the Gnu compiler is
unable to optimise over separate files.
